A Speculative Approach to Parallelization in Particle Swarm Optimization

### 2011-11-26 masters_thesis/si_paper/paper.tex
Packaged the files for the editors

\bibliographystyle{apa-good}
\bibliography{%
../../../bib/aml/bib,%
../../../bib/nfl/bib,%
../../../bib/optimization/bib,%
../../../bib/parallel/bib,%
../../../bib/pso/general/bib,%
../../../bib/pso/parallel/bib,%
../../../bib/pso/fips/bib,%
../../../bib/pso/topology/bib,%
../../../bib/sim-anneal/parallel/bib,%
../../../bib/ga/bib}

>>>>

\bibliographystyle{apa-good}
\bibliography{bib}
%../../../bib/aml/bib,%
%../../../bib/nfl/bib,%
%../../../bib/optimization/bib,%
%../../../bib/parallel/bib,%
%../../../bib/pso/general/bib,%
%../../../bib/pso/parallel/bib,%
%../../../bib/pso/fips/bib,%
%../../../bib/pso/topology/bib,%
%../../../bib/sim-anneal/parallel/bib,%
%../../../bib/ga/bib}
